Initial Analysis

### 2019-09-17 Initial_Analysis.Rmd
Trying to figure out Cotdevor

### Current issues

- How to distinguish between North and South? Example of Brazil, Uruguay and French Guyana

@@

@@

This function Read in species distribution from the observation data, ESM models and SAU data, still missing DBEM

@@

#### For testing 
# Spp <- 600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Spp <- 600464 # Discrete species 
# Spp <- 600051 # One of Pierrs massive (wrong) discrete spp
# x <- c(600464, # Discreat spp in one nation
      # 600059, # nowhere to be found spp
       # 601352, # Discrete spp in two nations
       # 600004) # transboundary spp
# Model <- "All"
# Coord <- CoorG
# 
# # For EEZ
Neighbours <- Neighbours_Data
Index_Code <- Index_Code
#  
# __________________________________
# __________________________________

@@

  EstTransIndex=Current_Spp
    print(To_Print)
  }

@@

# Determine forlder for saving results
Folder <- "Trans_Results"
Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "")

@@

  # Set the path for each file
  Distpath <- paste(Results_Path,"/Trans_Results/",Spp,sep="")

@@

# Updates result's path for the jurisdiction
Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")

@@

  # List of species
  Spp <- list.files(paste(Results_Path,"/Trans_Results",sep=""))[-829]

@@

# Data per Territory
Transboundary_Spp <- Tresholded_Data %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    )

@@

head(World_sf_si)
head(World_sf_si_land)

unique(World_sf_si$Bins)
unique(World_sf_si_land$BinsLan)

@@

# Get the NA's to be grey
Grey_land <- World_sf_si_land %>% 
  filter(is.na(BinsLan))

Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = BinsLan), colour = "grey80") +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = BinsLan),fill = "grey80") + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
                               # rev(wes_palette(n = 4, name = "Darjeeling2"))
                               # ),
                     # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
                     na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

@@

Data <- World_sf_si_land %>% 
  as_tibble() %>% 
  select(Territory, BinsLan)

Data_EEZ <- World_sf_si %>% 
  as_tibble() %>% 
  select(Territory, Bins)

### EEZ shapefile
eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks

eez = spTransform(eez, CRS("+proj=longlat"))
eez = spTransform(eez, CRS("+proj=wintri"))
eez = fortify(eez)

World_sf_si <- World_sf %>%
  st_transform(crs = 4326

#### Round map tryout 
mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))

mapworld<- mapworld %>% 
  rename(Territory = id) %>% 
  left_join(Data,
            by = "Territory") %>% 
  left_join(Data_EEZ,
            by = "Territory") %>% 
  rename(id = Territory)

# head(mapworld)

#create map boundary
ll.to.wt <- function (points)
  as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
                            CRS("+proj=wintri")))

lseq = seq(-85, 85, by=.25)
boundary <- ll.to.wt(data.frame(
  long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
  lat  = c(lseq,                    rev(lseq),          lseq[1])))

# New facet label names for dose variable
ggplot()+
  geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
  geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
  geom_polygon(data = mapworld, 
               aes(
                 x = long,
                 y = lat,
                 group = group,
                 fill = BinsLan
               ),
               colour="grey") +
  geom_polygon(data = mapworld, 
               aes(
                 x = long,
                 y = lat,
                 group = group,
                 fill = Bins)
               ) +
  geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
  # geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
  # geom_text_repel(data=ui,aes(x=long, y=lat, label=un.name), size=2.5, color = 'black',
  #                 box.padding = unit(0.5, "lines"),
  #                 point.padding = unit(0.5, "lines"),
  #                 segment.color = 'grey50') +
  scale_radius(range = c(1, 2)) #+
  # scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
  # theme_map()+
#   theme(legend.key = element_blank(),
#         strip.background = element_blank(),
#         legend.position = "none",
#         text = element_text(size=12,face="bold"))+
#   facet_wrap(~variable, scales = "free", ncol=1)+scale_shape(guide=FALSE)+scale_size(guide=FALSE)
# y=tag_facet(q, tag_pool = c("d","e","f"))

@@

>>>>

@@

### Determine species list

@@

This function Read in species distribution from the observation data, ESM models and SAU data

@@

#### For testing 
# Spp <- 600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Spp <- 600464 # Discrete species 
# Spp <- 600051 # One of Pierrs massive (wrong) discrete spp
# x <- c(600464, # Discreat spp in one nation
      # 600059, # nowhere to be found spp
       # 601352, # Discrete spp in two nations
       # 600004) # transboundary spp
# Model <- "All"
# Coord <- CoorG
# 
# # For EEZ
# Neighbours <- Neighbours_Data
# Index_Code <- Index_Code
#  
# __________________________________
# __________________________________

@@

  EstTransIndex=Current_Spp

@@

# Determine forlder for saving results
Folder <- "Trans_Results"
Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,sep = "/")

@@

  # Set the path for each file
  Distpath <- paste(Results_Path,Spp,sep="")

@@

# Set Jurisdiction to EEZ or RFMO
Jurisdiction <- "EEZ"
Folder <- "Trans_Results"

# Updates result's path for the jurisdiction
Results_Path <- paste(Results_Path,Jurisdiction,"/",Folder,"/",sep="")

@@

  # List of species
  Spp <- list.files(paste(Results_Path,sep=""))[-829]

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    )

@@

# head(World_sf_si)
# head(World_sf_si_land)

# unique(World_sf_si$Bins)
# unique(World_sf_si_land$BinsLan)

@@

# Get the NA's to be grey
Grey_land <- World_sf_si_land %>% 
  filter(is.na(Bins))

Plot <- ggplot() +
  # geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80") +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80") + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
                               rev(wes_palette(n = 4, name = "Darjeeling2"))
                               ),
                     na.value = "white"
  ) +
  # scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
                     # na.value = "white"
  # ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

@@

# Data <- World_sf_si_land %>% 
#   as_tibble() %>% 
#   select(Territory, BinsLan)
# 
# Data_EEZ <- World_sf_si %>% 
#   as_tibble() %>% 
#   select(Territory, Bins)
# 
# 
# ### EEZ shapefile
# eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
# 
# eez = spTransform(eez, CRS("+proj=longlat"))
# eez = spTransform(eez, CRS("+proj=wintri"))
# eez = fortify(eez) 
# 
# World_sf_si <- World_sf %>%
#   st_transform(crs = 4326
# 
# #### Round map tryout 
# mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
# 
# mapworld<- mapworld %>% 
#   rename(Territory = id) %>% 
#   left_join(Data,
#             by = "Territory") %>% 
#   left_join(Data_EEZ,
#             by = "Territory") %>% 
#   rename(id = Territory)
# 
# # head(mapworld)
# 
# #create map boundary
# ll.to.wt <- function (points)
#   as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
#                             CRS("+proj=wintri")))
#  
# lseq = seq(-85, 85, by=.25)
# boundary <- ll.to.wt(data.frame(
#   long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
#   lat  = c(lseq,                    rev(lseq),          lseq[1])))
#  
# # New facet label names for dose variable
# ggplot()+
#   geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
#   geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
#   geom_polygon(data = mapworld, 
#                aes(
#                  x = long,
#                  y = lat,
#                  group = group,
#                  fill = BinsLan
#                ),
#                colour="grey") +
#   geom_polygon(data = mapworld, 
#                aes(
#                  x = long,
#                  y = lat,
#                  group = group,
#                  fill = Bins)
#                ) +
#   geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
  # geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
  # geom_text_repel(data=ui,aes(x=long, y=lat, label=un.name), size=2.5, color = 'black',
  #                 box.padding = unit(0.5, "lines"),
  #                 point.padding = unit(0.5, "lines"),
  #                 segment.color = 'grey50') +
  # scale_radius(range = c(1, 2)) #+
  # scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
  # theme_map()+
#   theme(legend.key = element_blank(),
#         strip.background = element_blank(),
#         legend.position = "none",
#         text = element_text(size=12,face="bold"))+
#   facet_wrap(~variable, scales = "free", ncol=1)+scale_shape(guide=FALSE)+scale_size(guide=FALSE)
# y=tag_facet(q, tag_pool = c("d","e","f"))

@@

### Côte de Ivory missing data

For some reason Côte de ivory is missing data. It was fixed at the begining when I was averaging 1951 to 1961 instead of 2004 to 2014, but now is somehow back to cero.

```{Cote_Deivory, eval =F, echo =F}

# It might be a problem in the name côte de'ivory....
# Nope, both INDEX and neighbours datasets are names alike

# Run getSppDistribution function with this:
Model="All"
Coord=CoorG

Spp <- 600423 #This species should work
